\chapter*{ABSTRACT}
\begin{center}
  \large
  \textbf{\emph{MINTING NFT ON SOLANA BLOCKCHAIN FOR MUSIC CONCERT TICKETS IN A MARKETPLACE USING SMART CONTRACTS BASED ON WEB3.0}}
\end{center}
% Menyembunyikan nomor halaman
\thispagestyle{empty}

\begin{flushleft}
  \setlength{\tabcolsep}{0pt}
  \bfseries
  \begin{tabular}{lc@{\hspace{6pt}}l}
  Student Name / NRP&: &Rianco Marcellino Andreas / 5024211061\\
  Department&: &Computer Engineering FTEIC - ITS\\
  Advisor&: &1. Mochamad Hariadi, S.T., M.Sc., Ph.D\\
  & & 2. Dr. Susi Juniastuti, S.T., M.Eng.\\
  \end{tabular}
  \vspace{4ex}
\end{flushleft}

\textbf{Abstract}

The music concert ticketing industry faces significant challenges related to ticket counterfeiting, illegal reselling, and lack of transparency. This research proposes the development of a minting system for Non-Fungible Tokens (NFTs) based on the \textit{Solana Blockchain} for music concert tickets, aiming to address these issues. The primary focus of this research is to optimize the NFT minting process to enhance the efficiency, security, and scalability of the digital ticketing system. The methodology includes designing and implementing \textit{smart contracts} on the \textit{Solana} platform, developing a \textit{Web3.0} interface for user interaction, and optimizing the minting process to reduce \textit{gas fees} and improve throughput. The proposed system is tested through high-load simulations and limited user trials to evaluate performance and usability. The expected outcomes include significant improvements in ticket security and authentication, more efficient secondary sales management, and an enhanced user experience in purchasing and utilizing digital concert tickets. This research also aims to provide insights into the integration of \textit{Solana Blockchain} and \textit{Web3.0} technologies within the entertainment industry. The key contribution of this research is the development of an optimized NFT minting system for music concert tickets, which has the potential to transform the management and distribution of digital tickets. The findings are expected to lay the foundation for broader adoption of \textit{blockchain} technology in ticketing and pave the way for further innovation in digital concert experiences.

\vspace{2ex}
\noindent
\textbf{Keywords: \emph{NFT, Solana Blockchain, Digital Concert Tickets, Smart Contracts, Web3.0, Minting Optimization}}
